Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-23 manuscript/manuscript.tex
Changes in manuscript

The spherical prisms known as tesseroids are mass elements defined in a geocentric spherical coordinate system bounded by a pair of parallels, a pair of  meridians, and two concentric spherical surfaces.
We define an external computation point $P(r, \phi, \lambda)$ where the gravity fields generated by the tesseroid are going to be calculated with respect to the local north oriented Cartesian coordinate system located at $P$.
In the special case of homogeneous density, the gravity potential, gradient and Marussi tensor components can be calculated through the integrals obtained by \citet{Grombein2013} \citep[see also][]{Uieda2016}.

In our case, we will suppose that the tesseroid has an arbitrary variable density in depth, i.e. only depends on the radius spherical coordinate.
Thus, the integrals for the gravity fields are slightly modified:

@@

For example, if we use a second order GLQ, the roots of the $P_2(x)$ Legendre polynomial and its corresponding weights are $x_i = \pm 0.577350269$ and $W_i = 1$, respectively.

@@

In order to test the accuracy of the GLQ approximation, \citet{Uieda2016} and \citet{Grombein2013} have compared the computed gravity fields with the ones generated by a spherical shell, the exceptional case with analytical solution \citep{Mikuska2006,Grombein2013}.

In case of variable density tesseroids, the comparison must obviously be made with a variable density spherical shell, whose analytical solution will depend on the chosen density function.
Because the literature has not offered it yet, we needed to develop it ourselves.

Lets consider a spherical shell with inner and outer radii $R_1$ and $R_2$, respectivetly, which density depends on the radius spherical coordinate (Figure \ref{fig:spherical-shell}).
The gravity potential generated by the shell on an arbitrary external point $Q(0,0,r)$, located along the $z$ axe at a distance $r$ from the origin, can be written as follows:

@@

\noindent where $\ell$ is defined as in equation \ref{eq:ell}.
The computation point $Q$ is located at latitude $\phi=90^\circ$, so $\ell$ and $\cos\psi$ (defined in equation \ref{eq:cospsi}) get simplified:

>>>>

The spherical prisms known as tesseroids are mass elements defined in a geocentric spherical coordinate system bounded by a pair of parallels, a pair of  meridians, and two concentric spherical surfaces.
We define an external computation point $P(r, \phi, \lambda)$ where the gravity fields generated by the tesseroid are going to be calculated with respect to the local north oriented Cartesian coordinate system located at $P$.
In the special case of homogeneous density, the gravity potential, its gradient and the Marussi tensor components can be calculated through the integrals obtained by \citet{Grombein2013} \citep[see also][]{Uieda2016}.

In our case, we will assume that the tesseroid has an arbitrary variable density in depth, i.e. only depends on the radius spherical coordinate.
Thus, the integrals for the gravity fields are slightly modified:

@@

For example, if we use a second order GLQ, the roots of the $P_2(x)$ Legendre polynomial and its corresponding weights are $x_i = \pm 0.577350269$ and $W_i = 1$.

@@

In order to test the accuracy of the GLQ approximation, \citet{Uieda2016} and \citet{Grombein2013} have compared the numerical model with the analytical solution of the gravity fields generated by a spherical shell with homogeneous density, the exceptional case with analytical solution \citep{Mikuska2006,Grombein2013}.

In case of variable density tesseroids, the comparison must obviously be made with a variable density spherical shell, whose analytical solution will depend on the chosen density function.
Because the literature has not offered it yet, we needed to develop it ourselves. \todo{ no se si ponerlo asi}

Lets consider a spherical shell with inner and outer radii $R_1$ and $R_2$, respectivetly, whose density depends on the radius spherical coordinate (Figure \ref{fig:spherical-shell}).
The gravity potential generated by the shell on an arbitrary external point $Q(0,0,r)$, located along the $z$ axe at a distance $r$ from the origin, can be written as follows:

@@

\noindent where $\ell$ is defined in equation \ref{eq:ell}.
The computation point $Q$ is located at latitude $\phi=90^\circ$, so $\ell$ and $\cos\psi$ (defined in equation \ref{eq:cospsi}) get simplified:
